IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-05-10 codes/R/paper/cohorts_nc.Rnw
add all tables

read_chunk(here("codes/R/1_load.R"))
read_chunk(here("codes/R/2_efa.R"))
read_chunk(here("codes/R/3_inv_main.R"))
read_chunk(here("codes/R/3_inv_aux.R"))
read_chunk(here("codes/R/3_inv_fit.R"))
read_chunk(here("codes/R/4_scores.R"))
read_chunk(here("codes/R/4_scores_aux.R"))
read_chunk(here("codes/R/5_graphs.R"))
read_chunk(here("codes/R/6_decvars.R"))
read_chunk(here("codes/R/7_counterf.R"))
read_chunk(here("codes/R/7_counterf_graphs.R"))
read_chunk(here("codes/R/7_counterf_tabs.R"))
read_chunk(here("codes/R/7_counterf_seqdec.R"))
read_chunk(here("codes/R/getpars.R"))

@@

% 
% \begin{figure}
% <<FACINEQ, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=12, fig.width=10, out.width='1\\linewidth'>>=
% @
% \caption{Mean scores across income quintiles}\label{fig:meanci}
% {\scriptsize \emph{Notes}: The figure plots the mean and its 95\% confidence interval across the quintiles in the income distribution. \par}
% \end{figure}

@@

<<FORMULAS>>=
# define variables and formulas for regression and decomposition
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \begin{table}
% \caption{Quantifying the gradient}
% \centering
% \resizebox{\textwidth}{!}{
% <<FA_REGS_REAL_M, results='asis'>>=
% # regress scores on income
% library(stargazer)
% 
% decvars_reg <- c(decvars, "cohort") # add cohort
% interact_reg <- paste0(decvars_reg[! decvars_reg %in% c("cohort")], "*cohort")
% 
% form_ext_reg <- as.formula(paste("EXT ~ ", paste0(decvars2, collapse = '+')))
% form.ext2i <- as.formula(paste("EXT ~ ", paste0(c(decvars2, interact2), collapse = '+')))
% form.int2 <- as.formula(paste("INT ~ ", paste0(decvars2, collapse = '+')))
% form.int2i <- as.formula(paste("INT ~ ", paste0(c(decvars2, interact2), collapse = '+')))
% 
% r.ext.m  <- lm(form.ext2,  data=subset(scores2plot, sex=="M"))
% r.exti.m <- lm(form.ext2i, data=subset(scores2plot, sex=="M"))
% r.ext.f  <- lm(form.ext2,  data=subset(scores2plot, sex=="F"))
% r.exti.f <- lm(form.ext2i, data=subset(scores2plot, sex=="F"))
% r.int.m  <- lm(form.int2,  data=subset(scores2plot, sex=="M"))
% r.inti.m <- lm(form.int2i, data=subset(scores2plot, sex=="M"))
% r.int.f  <- lm(form.int2,  data=subset(scores2plot, sex=="F"))
% r.inti.f <- lm(form.int2i, data=subset(scores2plot, sex=="F"))
% 
% stargazer(r.ext.m, r.exti.m, r.ext.f, r.exti.f, r.int.m, r.inti.m, r.int.f, r.inti.f,
%           column.labels=c("M","M","F","F","M","M","F","F"), #,"BCS F","MCS F","BCS F","MCS F"),
%           dep.var.caption = "", multicolumn = FALSE,
%           #omit=c("Constant", paste0("region", c(2:9))),
%           no.space=TRUE,
%           omit.stat= c("rsq", "f", "ser", "aic", "ll"),
%           notes = "All estimates control for Government Office Region of birth.",
%           single.row=TRUE,
%           float=FALSE    # needs begin table outside it
% )
% @
% }
% \end{table}

@@

<<COUNTERF_SEQDEC_PREP>>=
# data for decomposition plots
@

@@

\begin{landscape}
\begin{figure}
<<COUNTERF_SEQDEC_EXT, dependson='COUNTERF_SEQDEC_PREP', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.seqdec.ext
@
\caption{Counterfactual sequential decomposition -- externalising skills}\label{fig:counterf_seq_ext}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
<<COUNTERF_SEQDEC_INT, dependson='COUNTERF_SEQDEC_PREP', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.seqdec.int
@
\caption{Counterfactual sequential decomposition -- internalising skills}\label{fig:counterf_seq_int}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}

>>>>

read_chunk(here("codes/R/1_load.R"))
read_chunk(here("codes/R/2_efa.R"))
read_chunk(here("codes/R/3_inv_main.R"))
read_chunk(here("codes/R/3_inv_aux.R"))
read_chunk(here("codes/R/3_inv_fit.R"))
read_chunk(here("codes/R/4_scores.R"))
read_chunk(here("codes/R/4_scores_aux.R"))
read_chunk(here("codes/R/5_graphs.R"))
read_chunk(here("codes/R/6_selectvars.R"))
read_chunk(here("codes/R/7_counterf.R"))
read_chunk(here("codes/R/7_counterf_graphs.R"))
read_chunk(here("codes/R/7_counterf_tabs.R"))
read_chunk(here("codes/R/7_counterf_seqdec.R"))
read_chunk(here("codes/R/8_regs.R"))
read_chunk(here("codes/R/getpars.R"))

@@

@@

<<SELECTVARS>>=
# define variables and formulas for regression and decomposition
@

<<REGRESSIONS, dependson="SELECTVARS">>=
# run all regression models
@

\begin{table}
\caption{Quantifying the gradient -- Males externalising}
\centering
\resizebox{\textwidth}{!}{
<<REGS_EXT_M, results='asis', dependson="REGRESSIONS">>=
library(stargazer)
stargazer(r.ext$BCS.M[[1]], r.ext$BCS.M[[2]], r.ext$BCS.M[[3]], r.ext$MCS.M[[1]], r.ext$MCS.M[[2]], r.ext$MCS.M[[3]],
          column.labels=c("BCS","BCS","BCS","MCS","MCS","MCS"),
          dep.var.caption = "", multicolumn = FALSE,
          #omit=c("Constant", paste0("region", c(2:9))),
          no.space=TRUE,
          omit.stat= c("f", "ser", "aic", "ll"),
          #notes = "All estimates control for Government Office Region of birth.",
          single.row=TRUE,
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}

\begin{table}
\caption{Quantifying the gradient -- Females externalising}
\centering
\resizebox{\textwidth}{!}{
<<REGS_EXT_F, results='asis', dependson="REGRESSIONS">>=
library(stargazer)
stargazer(r.ext$BCS.F[[1]], r.ext$BCS.F[[2]], r.ext$BCS.F[[3]], r.ext$MCS.F[[1]], r.ext$MCS.F[[2]], r.ext$MCS.F[[3]],
          column.labels=c("BCS","BCS","BCS","MCS","MCS","MCS"),
          dep.var.caption = "", multicolumn = FALSE,
          #omit=c("Constant", paste0("region", c(2:9))),
          no.space=TRUE,
          omit.stat= c("f", "ser", "aic", "ll"),
          #notes = "All estimates control for Government Office Region of birth.",
          single.row=TRUE,
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}

\begin{table}
\caption{Quantifying the gradient -- Males internalising}
\centering
\resizebox{\textwidth}{!}{
<<REGS_INT_M, results='asis', dependson="REGRESSIONS">>=
library(stargazer)
stargazer(r.int$BCS.M[[1]], r.int$BCS.M[[2]], r.int$BCS.M[[3]], r.int$MCS.M[[1]], r.int$MCS.M[[2]], r.ext$MCS.M[[3]],
          column.labels=c("BCS","BCS","BCS","MCS","MCS","MCS"),
          dep.var.caption = "", multicolumn = FALSE,
          #omit=c("Constant", paste0("region", c(2:9))),
          no.space=TRUE,
          omit.stat= c("f", "ser", "aic", "ll"),
          #notes = "All estimates control for Government Office Region of birth.",
          single.row=TRUE,
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}

\begin{table}
\caption{Quantifying the gradient -- Females internalising}
\centering
\resizebox{\textwidth}{!}{
<<REGS_INT_F, results='asis', dependson="REGRESSIONS">>=
library(stargazer)
stargazer(r.int$BCS.F[[1]], r.int$BCS.F[[2]], r.int$BCS.F[[3]], r.int$MCS.F[[1]], r.int$MCS.F[[2]], r.int$MCS.F[[3]],
          column.labels=c("BCS","BCS","BCS","MCS","MCS","MCS"),
          dep.var.caption = "", multicolumn = FALSE,
          #omit=c("Constant", paste0("region", c(2:9))),
          no.space=TRUE,
          omit.stat= c("f", "ser", "aic", "ll"),
          #notes = "All estimates control for Government Office Region of birth.",
          single.row=TRUE,
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}

\begin{landscape}
\begin{table}
\caption{Effect of behavioural skills on adolescent outcomes -- BCS males}
\centering
\resizebox{24cm}{!}{
<<REGS_OUTC_BCS_M, results='asis', dependson="REGRESSIONS">>=
library(stargazer)
# get mean dependent vars
dvmeans <- colMeans(bcsoutc[bcsoutc$sex=="F",bcsoutcvars], na.rm = T)
dvmeans <- round(unlist(lapply(dvmeans, function(x) rep(x,2))),3)

stargazer(bcsoutcmod_m_uc[[1]], bcsoutcmod_m_c[[1]],
          bcsoutcmod_m_uc[[2]], bcsoutcmod_m_c[[2]],
          bcsoutcmod_m_uc[[3]], bcsoutcmod_m_c[[3]],
          bcsoutcmod_m_uc[[4]], bcsoutcmod_m_c[[4]],
          bcsoutcmod_m_uc[[5]], bcsoutcmod_m_c[[5]],
          bcsoutcmod_m_uc[[6]], bcsoutcmod_m_c[[6]],
          add.lines = list(c("Mean Dep Var", dvmeans)),
          no.space=TRUE,
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          single.row=T,
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}
\end{landscape}

\begin{landscape}
\begin{table}
\caption{Effect of behavioural skills on adolescent outcomes -- MCS males}
\centering
\resizebox{24cm}{!}{
<<REGS_OUTC_MCS_M, results='asis', dependson="REGRESSIONS">>=
library(stargazer)
# get mean dependent vars
dvmeans <- colMeans(mcsoutc[mcsoutc$sex=="F",mcsoutcvars], na.rm = T)
dvmeans <- round(unlist(lapply(dvmeans, function(x) rep(x,2))),3)

stargazer(mcsoutcmod_m_uc[[1]], mcsoutcmod_m_c[[1]],
          mcsoutcmod_m_uc[[2]], mcsoutcmod_m_c[[2]],
          mcsoutcmod_m_uc[[3]], mcsoutcmod_m_c[[3]],
          mcsoutcmod_m_uc[[4]], mcsoutcmod_m_c[[4]],
          mcsoutcmod_m_uc[[5]], mcsoutcmod_m_c[[5]],
          add.lines = list(c("Mean Dep Var", dvmeans)),
          no.space=TRUE,
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          single.row=T,
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}
\end{landscape}

\begin{landscape}
\begin{table}
\caption{Effect of behavioural skills on adolescent outcomes -- BCS females}
\centering
\resizebox{24cm}{!}{
<<REGS_OUTC_BCS_F, results='asis', dependson="REGRESSIONS">>=
library(stargazer)
# get mean dependent vars
dvmeans <- colMeans(bcsoutc[bcsoutc$sex=="F",bcsoutcvars], na.rm = T)
dvmeans <- round(unlist(lapply(dvmeans, function(x) rep(x,2))),3)

stargazer(bcsoutcmod_f_uc[[1]], bcsoutcmod_f_c[[1]],
          bcsoutcmod_f_uc[[2]], bcsoutcmod_f_c[[2]],
          bcsoutcmod_f_uc[[3]], bcsoutcmod_f_c[[3]],
          bcsoutcmod_f_uc[[4]], bcsoutcmod_f_c[[4]],
          bcsoutcmod_f_uc[[5]], bcsoutcmod_f_c[[5]],
          bcsoutcmod_f_uc[[6]], bcsoutcmod_f_c[[6]],
          add.lines = list(c("Mean Dep Var", dvmeans)),
          no.space=TRUE,
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          single.row=T,
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}
\end{landscape}

\begin{landscape}
\begin{table}
\caption{Effect of behavioural skills on adolescent outcomes -- MCS females}
\centering
\resizebox{24cm}{!}{
<<REGS_OUTC_MCS_F, results='asis', dependson="REGRESSIONS">>=
library(stargazer)
# get mean dependent vars
dvmeans <- colMeans(mcsoutc[mcsoutc$sex=="F",mcsoutcvars], na.rm = T)
dvmeans <- round(unlist(lapply(dvmeans, function(x) rep(x,2))),3)

stargazer(mcsoutcmod_f_uc[[1]], mcsoutcmod_f_c[[1]],
          mcsoutcmod_f_uc[[2]], mcsoutcmod_f_c[[2]],
          mcsoutcmod_f_uc[[3]], mcsoutcmod_f_c[[3]],
          mcsoutcmod_f_uc[[4]], mcsoutcmod_f_c[[4]],
          mcsoutcmod_f_uc[[5]], mcsoutcmod_f_c[[5]],
          add.lines = list(c("Mean Dep Var", dvmeans)),
          no.space=TRUE,
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          single.row=T,
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}
\end{landscape}

@@

<<COUNTERF_SEQDEC_ESTIM, dependson="SELECTVARS">>=
# estimate sequential decompositions
@

<<COUNTERF_SEQDEC_PREP>>=
# extract data
@

@@

\begin{landscape}
\begin{figure}
<<COUNTERF_SEQDEC_EXT, dependson='COUNTERF_SEQDEC_PLOT', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.seqdec.ext
@
\caption{Counterfactual sequential decomposition -- externalising skills}\label{fig:counterf_seq_ext}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
<<COUNTERF_SEQDEC_INT, dependson='COUNTERF_SEQDEC_PLOT', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.seqdec.int
@
\caption{Counterfactual sequential decomposition -- internalising skills}\label{fig:counterf_seq_int}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}
